CannonRV: Measuring radial velocities with a data-driven spectral model

### 2017-01-26 paper/ms2.tex
re-construct the document
Re-construct the document and make a few new plots for individual
visits.

@@

\section{\label{sec:level1}Introduction}

Coming soon...

@@

 \section{\label{sec:level1}Assumption and method}
 \subsection{\label{sec:level2}Optimize the spectrum}

%{\AA}
Suppose we have a trained model. The training set contains 548 stellar and each stellar spectrum has 8575 pixels. Every pixel is related to a specific wave length. It belongs to APOGEE data release 10 and has a good quality. These stellar are the very same objects as used by the APOGEE survey for the calibration of DR10. Each of them has at least nine stellar labels. But in the training step, we only use three of them $T_{eff}$, $log$ g  and $\left[Fe/H\right]$. They span the range of $3500K <T_{eff}< 5300K$, $0 <log$ $g< 5$ and $-2.5 <\left[Fe/H\right]< 0.45$. The spectrum we use in the training and testing step of the cannon is the combined spectrum from aspcap files. The labels we use are from the Allstar visit file.

The model we adopt

@@

 Where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. 
 \(v(l_n)\) is the vectorizing function. 
The input \(l_n\) is the label list of length K for star n and the  output 
\(v(l_n)\) is a vector of length D (D is bigger than K).
\( \theta_{j}\) is a vector of length D of parameters which controlling the model at wavelength pixel j.
\( e_{jn}\) is a noise draw or residual at pixel j for star n.

\(l_n^{inf}\) and \( \theta_{j}\) are available after the training step.
Infer spectrum by using:

\begin{equation}
y_{jn}^{inf} = v(l_n^{inf}) \cdot \theta_{j} 
\end{equation}

 This is how to obtain the synthesized spectrum by using the Cannon 2. We also call it inferred flux(spectrum).

The Cannon 2 can predict the spectrum pretty well. But we can still improve it.
\bigskip

From the inferred spectrum \(y_{jn}^{inf}\), we optimize it and generate a better synthesized spectrum, which we call \(y_{jn}^{opt}\).
\bigskip

The method we use is to represent the spectrum at pixel j by using the inferred spectrum at pixel j-1,pixel j and pixel j+1.(If the pixel is out of range, set the flux as 1). The data we use is the same as the training step.
\bigskip

The new spectrum, which is the optimized spectrum, is represented by:

@@

We use the least chi-squared method. So our objective function is the chi-squared between the optimized spectrum and the spectrum data. The objective function for star n is:
\bigskip

@@

$\sigma_{jn}^2$ is the data uncertainty for star n at pixel j. The number of stellar and pixel each star are N and J. Here N and J are the number of the stellar and the number of pixel each star.  Write the objective function in the form of matrix can make it simpler. There will be N objective functions and N sets of a, b and c. So we introduce several matrix: $Y_n$, $A_n$, $C_n$ and $X_n$ for star n, which are defined as followed:

@@

By using (7) we can calculate $a_n$, $b_n$ and $c_n$, which are parameters a, b and c for star n. 
b should be much bigger than both a and c. And a+b+c should be equal to 1.

Calculate the optimized spectrum \( y_{j,n}^{opt}\) by using (3). The Experiment 1 shows that the optimization works.
\bigskip

%It works!

\subsection{\label{sec:level2}Spectrum calibration}
\bigskip
After the optimization, we obtain many sets of a, b and c. In our theory b should be close to 1 and a, c is much smaller than b. But the fact is that sometimes b is much smaller than and c. This is because of the spectral broadening in the measurement. The equipment is not perfect, so the resolution of the spectrum will become lower due to scattering, dispersion or other reasons. Then the spectrum will broaden and the real spectrum at pixel j is not what we obtain, it should be the spectrum at nearby pixels, which include pixel j-1 and j+1. Thus b will be smaller than a+c, which we will discuss in the following experiment 3.
\bigskip

Sometimes a or c will be much bigger than the other two parameters. This is also because of the measurement. Even we ignore the spectral broadening, the measured spectrum may move one pixel left or one pixel right from the real spectrum. If the measured spectrum move one pixel left, then a should be close to 1 and it's similar for c. The measured spectrum moves left or right is because of the error in the measured velocity, so there will be error in measuring the Doppler effect, which leads to a spectrum moving. We will show this in experiment 3.

We will do this optimization for each visit of every star in APOGEE DR10. The spectrum we use is in apstar file. We will re-analyze the velocities after the optimization and deliver back the velocities shift for the APOGEE data.
\bigskip

\subsection{\label{sec:level2} Interpret a, b, c in term of radial velocity}

%Can you interpret a, b, c in terms of radial velocity? If so, how?
After obtaining a, b and c for these stars, we can calibrate the errors in the radial velocities of the combined spectra of these stars. These combined spectra are stored in Apstar files, which are generated by different individual visits after resampling them onto a common, logarithmically-spaced wavelength scale, and after removing derived radial velocities of each visit. The apStar files also include the individual visit spectra, resampled and shifted to rest wavelength. If we need to use the individual visits before resampling, apVisit files are needed. In our experiment, we use the resampled spectrum in Apstar files. The radial velocities of the spectrum in Apstar files should be 0, but in fact they are not. This is because of the errors in radial velocity measurement by the APOGEE team. The APOGEE team determines the radial velocities of the stars by two steps.
\bigskip
\\
1. Estimate the radial velocity of each visit by cross-correlating the visit spectrum against a grid of synthetic spectra.
\\
2. Compare the spectrum of each visit with the combined spectrum and re-derive the radial velocity for each visit iteratively. 
\bigskip

After obtaining the velocities, the APOGEE team uses the de-Doppler wavelengths and resample the spectrum onto the final logarithmically-spaced wavelength scale by using sinc interpolation. Finally, generate the combined spectrum by using the spectrums of different visits. Both combined spectrum and each visit may have radial velocity errors because the synthetic spectra are not perfect.

We will derive these radial velocity errors, then de-Doppler them and resample the fluxes onto a common, logarithmically-spaced wavelength scale, which is the same as the wavelength scale in Apstar and ASPCAP flies.

@@

The data spectrum we use in experiment 1 to 4 is the combined spectrum and we start to use spectrum of each visit in experiment 5.

@@

We will plot the histogram for the five parameters in our experiment.

\subsection{\label{sec:level2} Obtain information from the individual exposures}

%How do you continuum-normalize the individual exposures, and can you demonstrate to me that your proposal of how to do that is working well?

Before deriving a, b and c for each visit, we need to continuum-normalize the spectrum of each visit. This is because the absolute value of each visit is different. Therefore, each visit spectrum needs to be roughly continuum normalized before they are combined. The APOGEE team uses a median filter to continuum-normalize the spectrum of each visit. 
\bigskip

Our method is the same as the one in Ness et al 2015. The spectrum for each visit is in Apstar files, which are already resampled onto the sample wavelength scale with 8575 pixels. First, cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]] to avoid gaps in the spectrum. Then, do pseudo-normalization in these three regions and obtain the pseudo-normalized flux and inverse variance. Third, put a mask on the spectrum. Finally, fit the continuum spectrum in the continuous regions by using a 3-order sinusoid function and obtain the continuum-normalized spectrum. Our method is different from the one used by the APOGEE team and we will demonstrate it works.

To check whether it works, we can look at the normalized spectrum of each visit. If the absolute value of the normalized flux for each visit is similar to each other, the normalization works.

Also, we can infer labels by using the normalized flux of each visit. If the inferred labels from each visit are similar to the ones from the combined spectrum, the normalization works. We define $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H as:

If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works.

The details are in experiment 5.

@@

 \section{\label{sec:level1}Experiment}
 \subsection{\label{sec:level2}Experiment 1}

Choose four stellar, which are not in the training set. Optimize the spectrum of these four stars and obtain a, b and c for each stars. The labels we use in the figures are from the Cannon, which means they are inferred labels.

The labels of the four stars are:
\begin{center}

 Star A  $T_{eff} =4750$  log g =3.0 $\left[Fe/h\right] =0.15$

 Star B  $T_{eff} =4849$  log g =2.2 $\left[Fe/h\right] =-1.0$

 Star C  $T_{eff} =3614$  log g =0.4 $\left[Fe/h\right] =-0.68$

 Star D  $T_{eff} =5003$  log g =2.8 $\left[Fe/h\right] =-0.71$

@@

\begin{table}[ht]
\caption{Fitting results for the four stars}
\centering
\begin{tabular}{c c c c c}
\hline\hline
Star Name & a & b & c & a+b+c \\ [0.5ex] % inserts table %heading
\hline
Star A & 0.121 & 0.824 & 0.052 & 0.998 \\
Star B & 0.176 & 0.541 &  0.278 & 0.995 \\
Star C & 0.003 & 1.004 &  -0.007 & 1.000 \\
Star D & -0.009  & 1.029 & -0.020 & 1.000 \\ [1ex]
\hline
\end{tabular}
\label{table:nonlin}
\end{table}

 Then plot the spectrum. The spectrum we use is the combined non-normalized spectrum from apstar files.

 The black line "Observed" is the observed spectrum from the data  \(y_{jn}\).
 The green line "inferred" is \( y_{j,n}^{inf}\) , which is generated by the Cannon 2.
 The red line "optimized" is \( y_{j,n}^{opt}\), which is generated by (3)

@@

\begin{center}
\includegraphics[width=170mm]{figure_1.png}
\end{center}
 \centerline{Fig.1 The spectrum of Star A, B, C and D}

 \centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
\bigskip

Finally compare the chi-square for these four stars of the two methods:
The total chi-squared of the four stars becomes 2\% smaller, which means our method works.

 \subsection{\label{sec:level2}Experiment 2}
 Plot the parameters a, b and c vs the number of the star. 
 \bigskip

In experiment 1, we use only four stars to obtain parameters a, b and c and the result is pretty good.  What if we optimize more stars? We randomly choose about 1\% of the APOGEE DR10 and make a histogram plot. The mean inverse variance of the stars is bigger than 10000 but smaller than 40000. We also exclude stars with undetermined labels. (The label is set to -10000 if it's not determined.)The number of stars is 614. Now parameters a, b and c are obtained from independent stars, which means the objective function only contain the chi-squared of one star and there will be 614 objective functions. And there will be 614 sets of a, b and c. The spectrum we use is the combined non-normalized spectrum from apstar files. And soon we will use the individual visit non-normalized spectrum from apstar files. Before using these spectrum, normalization is needed. The normalization method we use is the same as the one in Ness et al 2015. The labels we use are from the Cannon, which means they are inferred labels.

We plot a, b, c against the mean fiber number, which is the average fiber number of the spectrum we optimize. In APOGEE DR 10, the fiber number is between 1 and 640. The parameters we use are from figure 3

\begin{center}
\includegraphics[width=170mm]{figure_2.png}
\end{center}

\centerline{Fig.2 a,b,c vs Mean Fiber Number}
\bigskip

This figure gives us information about the relation between parameters a, b, c and fiber number, which can be used to establish a data-driven spectrum calibration model.
\bigskip

We also plot delta-chi-squared vs Mean Fiber number, where delta-chi-squared is the difference between the chi-squared of the spectrum before our optimization and after. It should be bigger than 0.

\begin{center}
\includegraphics[width=170mm]{figure_3.png}
\end{center}

\centerline{Fig.3 Delta-chi-squared vs Mean Fiber Number}
\bigskip

\subsection{\label{sec:level2}Experiment 3}

\bigskip
Now choose some examples from the 614 stars and make some plots.Sometimes the inferred spectrum doesn't look like the data, which is already described in Ness et al 2015. We don't use these stars in the plots.

First, plot the four stars with biggest delta-chi-squared and smallest delta-chi-squared:

\begin{center}
\includegraphics[width=170mm]{figure_4.png}
\end{center}

\centerline{Fig.4 Spectrum of the four stars with biggest delta-chi-squared. }

\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}

\begin{center}
\includegraphics[width=170mm]{figure_5.png}
\end{center}

\centerline{Fig.5 Spectrum of the four stars with smallest delta-chi-squared. }

\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
\bigskip

From figure 6 and 7, we find that the four stars with smallest delta-chi-squared have b closer to 1, but the four stars with biggest delta-chi-squared don't.

Also, we want to look into the spectral broadening.
Plot four stars with b closest to 1:

\begin{center}
\includegraphics[width=170mm]{figure_6.png}
\end{center}

\centerline{Fig.6 Spectrum of the four stars with b closest to 1. }

\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
\bigskip

From the histogram of a, b and c, we also find that sometimes b becomes much smaller than a+c, which means the spectrum is broadening due to the measurement. The resolution of the spectrum becomes lower and this is what we want to calibrate.
\bigskip
Here is the plot of the four stars with biggest a+c-b:

\begin{center}
\includegraphics[width=170mm]{figure_7.png}
\end{center}

\centerline{Fig.7 Spectrum of the four stars with biggest a+c-b. }

\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
\bigskip

@@

We found a and c are close to 1, which is in accordance with our theory. 
Also, the optimized spectrum broaden when a+c is much bigger than b, which means the measured spectrum broaden due to the error in the measurement. This is what we need to calibrate.
\bigskip

To look deeper into the results, we also choose the four stars with biggest $a-c$ and biggest $c-a$. Then make another two plots:

\begin{center}
\includegraphics[width=170mm]{figure_8.png}
\end{center}

\centerline{Fig.8 Spectrum of the four stars with biggest $a-c$.}

\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
\bigskip

\begin{center}
\includegraphics[width=170mm]{figure_9.png}
\end{center}

\centerline{Fig.9 Spectrum of the four stars with biggest $c-a$.}

\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}

@@

For spectrum with $a>c$, the optimized spectrum moves left a little bit, which means the real spectrum should move right a little. It's similar for $c>a$. The c>a branch is not as obvious as the a>c branch.

\subsection{\label{sec:level2}Experiment 4}

\bigskip
We also plot the inferred labels $Teff$ against log g. The color bar shows the mean inverse variance of these stars.

\begin{center}
\includegraphics[width=170mm]{figure_10.png}
\end{center}

\centerline{Fig.10 $Teff$ vs $log g$}
\bigskip

\subsection{\label{sec:level2}Experiment 5}

Here we plot the histogram of the radial velocity shifts in figure 11 and the radial velocity shifts in figure 12. The data we use is the combined spectrums of the 614 stars in the former experiment.

\begin{center}
\includegraphics[width=170mm]{figure_11.png}
\end{center}

\centerline{Fig.11 Histogram of the radial velocity shifts in combined spectrums for the 614 stars. }
\centerline{We exclude the outliers which have velocity shifts bigger than 2000 m/s}
\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
\bigskip

\begin{center}
\includegraphics[width=170mm]{figure_12.png}
\end{center}

\centerline{Fig.12 Radial velocity shifts for combined spectrums of the 614 stars against mean fiber number}
\centerline{We exclude the outliers which have velocity shifts bigger than 2000 m/s}
\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
\bigskip

We also plot the four stars with biggest radial velocity shifts, which are in figure 13.

\begin{center}
\includegraphics[width=170mm]{figure_13.png}
\end{center}

\centerline{Fig.13 Spectrum of the four stars with biggest radial velocity shifts.}

\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}

@@

After that, we want to calibrate the radial velocity for each visit. To begin with, we need to check whether our normalization works in each visit. The method is to infer labels for each visit and compare them with the ones from the combined spectrum. If our normalization works, the inferred labels from each visit for the same star should be similar to the ones from the combined spectrum. We plot the histogram which shows the deviations of the inferred labels of each visit from the ones generated by the combined spectrum of the same star. The data we use is the 614 stars in experiment 1 to 4. If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works.

\begin{center}
\includegraphics[width=170mm]{figure_14.png}
\end{center}

\centerline{Fig.14 Histogram for Delta Teff}
\bigskip

\begin{center}
\includegraphics[width=170mm]{figure_15.png}
\end{center}

\centerline{Fig.15 Histogram for Delta logg}

\begin{center}
\includegraphics[width=170mm]{figure_16.png}
\end{center}

\centerline{Fig.16 Histogram for Delta Fe/H}
\bigskip

We can see that most of the deviations are close to 0, which means our normalization for each visit doesn't make the spectrum distort.

In figure 17 and 18, we plot the continuum-normalized fluxes of all visits for the first star in figure 8. There are 6 individual visits and 2 combined spectrums. So in figure 17 and 18, there are 8 fluxes. The bottom two are the combined spectrum and the other 6 are individual visits. We can see that the absolute value of the flux for each visit is similar to each other, which means our normalization works.

\begin{center}
\includegraphics[width=170mm]{figure_17.png}
\end{center}

\centerline{Fig.17 Comparison of each visit for the first star in figure 8.}
\centerline{The bottom two are the combined spectrum and the other 6 are individual visits. The red dots are continuum pixels }
\bigskip

\begin{center}
\includegraphics[width=170mm]{figure_18.png}
\end{center}

\centerline{Fig.18 Comparison of each visit for the first star in figure 8.}
\centerline{The bottom two are the combined spectrum and the other 6 are individual visits. The red dots are continuum pixels }
\bigskip

@@

 Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
 \bigskip

\begin{center}
\includegraphics[width=170mm]{d_figure_1.png}
\end{center}

\centerline{Diagnostic Fig.1 Histogram of a b c for apstar data (What we use now)}
\bigskip

\begin{center}
\includegraphics[width=170mm]{d_figure_2.png}
\end{center}

\centerline{Diagnostic Fig.2 Four fake stars with Gaussian wave pack spectrums}
\centerline{The green line is the template and the black line is the observation}
\bigskip

\begin{center}
\includegraphics[width=170mm]{d_figure_3.png}
\end{center}

\centerline{Diagnostic Fig.3 Spectrum of the four stars with biggest c-a}
\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
\bigskip

\begin{center}
\includegraphics[width=170mm]{d_figure_4.png}
\end{center}

\centerline{Diagnostic Fig.4 Spectrum of the four stars with biggest a-c}
\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}

\begin{center}
\includegraphics[width=170mm]{d_figure_5.png}
\end{center}

\centerline{Diagnostic Fig.5 Spectrum of the four stars with biggest a+c-2b}
\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
\bigskip

\begin{center}
\includegraphics[width=170mm]{d_figure_6.png}
\end{center}

\centerline{Diagnostic Fig.6 Spectrum of the four stars with b closest to 1}
\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
\bigskip

\begin{center}
\includegraphics[width=170mm]{d_figure_7.png}
\end{center}

\centerline{Diagnostic Fig.7 Radial velocity shifts}
\centerline{ $v_3$ is the RV shift obtained from a, b and c. $v_5$ is from the five parameters. $v$ is from a, b and c if $2b>a+c$ and $v$ = $v_5$ if $2b<a+c$}
\bigskip

>>>>

\bibliographystyle{abbrv}

@@

\section{\label{sec:level1}Abstract}

The Cannon is a powerful tool which can predict the stellar labels from fluxes, which is a data-driven machine learning model. Also, it can infer fluxes from the stellar labels. Here we use the Cannon as a tool to calibrate the radial velocities(RV) in APOGEE DR 10 by fitting the inferred fluxes with the data fluxes. Then we compare our RV shift result with the APOGEE team and conclude our method is better. The most important thing of this work is that we can calibrate the velocity by using a new method-use data-driven model to calibrate physical parameters without using physical model. This is quicker than better than traditional methods.

@@

 \section{\label{sec:level1}Assumption and method}

 \subsection{\label{sec:level2}Continuum normalization}
Since the Cannon need the spectrums to be normalized. The first thing we should do is to continuum normalize the combined spectrums and individual visits. The data we use is the Apstar files in APOGEE DR10, which include two combined spectrums and several individual visits and they are set to the same wavelength scale after removing the radial velocities derived by APOGEE team. There are 8575 pixels and the wave length is equally logarithmically-spaced. The wavelength starts at 1.514 $\mu m$ and ends at 1.696 $\mu m$.
\bigskip

Our method is the same as the one in Ness et al 2015. The spectrum for each visit is in Apstar files, which are already resampled onto the sample wavelength scale with 8575 pixels. First, cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]] to avoid gaps in the spectrum. Then, do pseudo-normalization in these three regions and obtain the pseudo-normalized flux and inverse variance. Third, put a mask on the spectrum. Finally, fit the continuum spectrum in the continuous regions by using a 3-order sinusoid function and obtain the continuum-normalized spectrum. Our method is different from the one used by the APOGEE team and we will demonstrate it works.
\bigskip

To check whether our normalization methods works, we will:

\begin{description}
  \item[1] Plot the continuum pixels for combined spectrum and individual visits, then check whether they are roughly cover the spectrum evenly.
  \item[2] Plot individual visits and compare them with the combined spectrum, they should have similar shape.
  \item[3] Infer stellar labels from the individual visits by using the Cannon and the inferred labels should be similar from the ones from the combined spectrum for the very same star.
\end{description}

For point 3
If the inferred labels from each visit are similar to the ones from the combined spectrum, the normalization works. We define $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H as:

If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works. The details are in Experiment 1.

\subsection{\label{sec:level2}Calibrate the spectrums}

%{\AA}
In this part we will introduce the Cannon 2, and then use a linear method to optimize the inferred spectrum. Finally calibrate both the combined spectrum and individual visits.
\bigskip

The very first thing we use is the Cannon 2. Suppose we have a trained Cannon model. The training set contains 548 stellar and each stellar spectrum has 8575 pixels. Every pixel is related to a specific wave length. It belongs to APOGEE data release 10 and has a good quality. These stellar are the very same objects as used by the APOGEE survey for the calibration of DR10. Each of them has at least nine stellar labels. But in the training step, we only use three of them $T_{eff}$, $log$ g  and $\left[Fe/H\right]$. They span the range of $3500K <T_{eff}< 5300K$, $0 <log$ $g< 5$ and $-2.5 <\left[Fe/H\right]< 0.45$. In the training step, we only use the first combined spectrum for these 548 stars to train the model.
The model we adopt

@@

\begin{equation}
y_{jn}^{inf} = v(l_n^{inf}) \cdot \theta_{j} 
\end{equation}
\bigskip

Where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. 
 \(v(l_n)\) is the vectorizing function. 
The input \(l_n\) is the label list of length K for star n and the  output 
\(v(l_n)\) is a vector of length D (D is bigger than K).
\( \theta_{j}\) is a vector of length D of parameters which controlling the model at wavelength pixel j.
\( e_{jn}\) is a noise draw or residual at pixel j for star n.
$l_n$ and $l_n^{inf}$ are stellar labels and inferred stellar labels for star n.
$y_{jn}^{inf}$ is the inferred spectrum for star n at wavelength pixel j.

If we have a trained Cannon 2 model, $\theta_{j}$ is available. The labels we use are Teff, Log g and Fe/H. We randomly choose about 1\% of the APOGEE DR10 and make a histogram plot. The mean inverse variance of the stars is bigger than 10000 but smaller than 40000. We also exclude stars with undetermined labels. (The label is set to -10000 if it's not determined.)The number of stars is 614. Apply the Cannon 2 on these stars and obtain the inferred labels and inferred fluxes for them.

From the normalized combined spectrum and fluxes of individual visits for the very same star, several sets of inferred labels $l_n^{inf}$ are obtained. Then put the inferred labels $l_n^{inf}$ back into formula (5), the inferred combined spectrum and inferred fluxes of individual visits for star n is available. The data spectrum we use are in Apstar files. There are two combined spectrum and several individual visits in the Apstar files. Put all of these spectrum into the trained Cannon 2 and obtain several sets of inferred labels for each star. After that, put the inferred labels back into the model and calculate the inferred combined spectrum(There should be two) and inferred fluxes of individual visits. 
\bigskip

In the following step, we deal with the combined spectrum and individual visits with the same method. $y_{j,n}$ represents one spectrum of star n at pixel j. It can be either combined spectrum or individual visit.
\bigskip

The APOGEE team set the combined spectrum and fluxes of individual visits at rest by removing the radial velocities. However, since the derived radial velocities from the APOGEE team is not 100 \% correct, these fluxes are not at rest. There are radial velocity shifts between the radial velocities from the APOGEE team and the correct radial velocities. But we can assume the shifts of radial velocities are Gaussian distributed, so the inferred fluxes generated by the Cannon 2 are at rest. This means we can use inferred fluxes to calibrate the radial velocities derived by the APOGEE team. 
\bigskip

\begin{equation}
RV_{cor} = RV_{apo} + RV_{shift}
\end{equation}

Where $RV_{cor}$, $RV_{apo}$ and $RV_{shift}$ are the correct radial velocity, radial velocity from the APOGEE team and the radial velocity shift.
\bigskip

First, we define a spectrum called optimized spectrum.

@@

Where $y_{j,n}^{opt}$ is the optimized spectrum for star n at wavelength pixel j. We move the inferred spectrums one pixel left, 0 pixel and one pixel right to simulate the radial velocity shift of the data spectrum.

Then we fit the optimized spectrum to the data spectrum by using the least chi-squared method. After fitting the optimized spectrum to the data spectrum, we think the optimized spectrum has the very same radial velocity shift as the data spectrum. And we can derive the correct radial velocity of the spectrum by removing the radial velocity shift. So our objective function is the chi-squared between the optimized spectrum and the spectrum data. The objective function for star n is:
\bigskip

@@

$\sigma_{jn}^2$ is the data uncertainty for star n at pixel j. The number of stellar and pixel each star are N and J. Here N and J are the number of the stellar and the number of pixel each star.  Write the objective function in the form of matrix can make it simpler.

@@

By using (8) we can calculate $a_n$, $b_n$ and $c_n$, which are parameters a, b and c for one spectrum of star n.

% shall we put this part in Appendix
Calculate the optimized spectrum \( y_{j,n}^{opt}\) by using (4). The Experiment 2 shows that the optimization works.
\bigskip

%Can you interpret a, b, c in terms of radial velocity? If so, how?
After obtaining $a_n$, $b_n$ and $c_n$ for these stars, we can calibrate the combined spectra of these stars. These combined spectra are stored in Apstar files, which are generated by different individual visits after resampling them onto a common, logarithmically-spaced wavelength scale, and after removing derived radial velocities of each visit. There are two combined spectrums for one star, which are obtained by different method. The radial velocities of the spectrums in Apstar files should be 0, but in fact they are not. This is because of the errors in the radial velocity measurement by the APOGEE team.

@@

@@

We will plot the histogram for the five parameters in our experiment and demonstrate moving two pixels are good enough for these $2b<a+c$cases.

@@

 \section{\label{sec:level1}Experiment}

 \subsection{\label{sec:level2}Experiment 1}
To demonstrate the continuum normalization works well for the combined spectrums and individual visits, we plot the continuum pixels for stars with different SNR(signal to noise ratio), Teff and Logg. Here we randomly choose 5 stars with different SNR, Teff and logg and plot them in figure 1 to 5.

% star A
\bigskip

\begin{center}
\includegraphics[width=170mm]{CP_A.png}

\centerline{Fig.1 Comparison of each visit for Star A.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star A is 108. Teff = 4939K Logg =2.71 }

@@

% Star B
\bigskip

\begin{center}
\includegraphics[width=170mm]{CP_B.png}

\centerline{Fig.2 Comparison of each visit for Star B.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star B is 139. Teff = 4872K Logg =2.91 }

% Star C

@@

\begin{center}
\includegraphics[width=170mm]{CP_C.png}

\centerline{Fig.3 Comparison of each visit for Star C.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star C is 108. Teff = 4833K Logg =2.86 }

% Star D

@@

\begin{center}
\includegraphics[width=170mm]{CP_D.png}

\centerline{Fig.4 Comparison of each visit for Star D.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star D is 150. Teff = 4534K Logg =2.24 }

% Star E

@@

\begin{center}
\includegraphics[width=170mm]{CP_E.png}

\centerline{Fig.5 Comparison of each visit for Star E.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star E is 177. Teff = 4639K Logg =2.21 }

@@

We can also demonstrate the continuum normalization works by infer stellar labels from individual visits and compare them with one from the combined spectrum. Here we use formula 1, 2 and 3 to obtain delta-stellar labels. If they are very small, the normalization works. They are plotted in figure 6, 7 and 8.

\begin{center}
\includegraphics[width=170mm]{hist_d_teff.png}
\end{center}

\centerline{Fig.6 Histogram of Delta Teff for individual visits}
\bigskip

\begin{center}
\includegraphics[width=170mm]{hist_d_logg.png}
\end{center}

\centerline{Fig.7 Histogram of Delta logg for individual visits}

\begin{center}
\includegraphics[width=170mm]{hist_d_fe.png}
\end{center}

\centerline{Fig.8 Histogram of Delta Fe/H for individual visits}
\bigskip

We can see that these delta-stellar labels of individual visits are close to 0, which means the spectrums of individual visits don't change shape after the normalization. That's to say, the normalization works.

 \subsection{\label{sec:level2}Experiment 2}

 In experiment 2, we will focus on the parameters fitting for individual visits. First, we plot the histograms of parameters abc and RV shifts for individual visits.
\bigskip

\begin{center}
\includegraphics[width=170mm]{hist_abc_visits.png}
\end{center}

\centerline{Fig.9 Histogram of a,b,c for individual visits}
\bigskip

\begin{center}
\includegraphics[width=170mm]{hist_ve_visits.png}
\end{center}

\centerline{Fig.10 Histogram of RV shifts for individual visits}
\bigskip

Then, we try to find some relation between out results and FiberID, MJD(Modified Julia Date), RA and DEC. Figures 11, 12, 13, 14 and 15 shows the relation.

\begin{center}
\includegraphics[width=170mm]{dchi_vs_all.png}
\end{center}

\centerline{Fig.11 Delta-chi-squared vs MJD, FiberID, RA and DEC for individual visitis}
\bigskip

\begin{center}
\includegraphics[width=170mm]{a_vs_all.png}
\end{center}

\centerline{Fig.12 a vs MJD, FiberID, RA and DEC for individual visitis}
\bigskip

\begin{center}
\includegraphics[width=170mm]{b_vs_all.png}
\end{center}

\centerline{Fig.13 b vs MJD, FiberID, RA and DEC for individual visitis}
\bigskip

\begin{center}
\includegraphics[width=170mm]{c_vs_all.png}
\end{center}

\centerline{Fig.14 c vs MJD, FiberID, RA and DEC for individual visitis}
\bigskip

\begin{center}
\includegraphics[width=170mm]{ve_vs_all.png}
\end{center}

\centerline{Fig.15 RV shifts vs MJD, FiberID, RA and DEC for individual visitis}
\bigskip

Finally, we shows our RV shifts results are better than results from the APOGEE team. The evidences are in the following zoom-in plots.

@@

Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.

reference
\bibliography{t_1,pubext}
